\documentclass[letterpaper,10pt]{article}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}
\usepackage{lipsum}
\usepackage{xpatch}
\usepackage{geometry}

\newtoggle{full}
\toggletrue{full}
\togglefalse{full}

\renewcommand{\ttdefault}{ul9}
\xpatchcmd{\ttfamily}{\selectfont}{\fontencoding{T1}\selectfont}{}{}
\DeclareTextCommand{\nobreakspace}{T1}{\leavevmode\nobreak\ }

\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}% 
  \addtocounter{footnote}{-1}%
  \endgroup
}

\linespread{1.025}
\urlstyle{rm}

\def\name{Aijun Bai}
\def\footerlink{}

\hypersetup{
  colorlinks = true,
  urlcolor = blue,
  pdfauthor = {\name},
  pdfkeywords = {Aijun Bai, Curriculum Vitae},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9.2in},
  top=0.7in
}

\usepackage{etoolbox}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}

\usepackage{lastpage}
\usepackage{fancyhdr}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{Page \thepage\ of \pageref{LastPage}}

\pagestyle{fancy}

\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

\setlength\parindent{0em}

\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

\begin{flushleft}
	{\huge \name}
\end{flushleft}

\bigskip

\begin{minipage}{0.5\textwidth}
	Researcher, Microsoft Cloud \& AI \\
	One Microsoft Way, Redmond, WA 98052
\end{minipage}
%\hspace{0.5em}
\begin{minipage}{0.5\textwidth}
	\begin{tabular}{ll}
		Email:    & \href{mailto:aijun.bai@microsoft.com}{\rm aijun.bai@microsoft.com} \\
		Homepage: & \url{https://aijunbai.github.io/} \\
	\end{tabular}
\end{minipage}

\vspace{15pt}
\section*{Experience}
\begin{itemize}
	\item \textbf{Microsoft}, Cloud \& AI, Redmond, WA, United States, 2017.5 - present \\
	      \begin{tabular}{ll}
		      Position: & Researcher             \\
		      Project:  & Cognition intelligence \\
	      \end{tabular} \\
	\item \textbf{University of California at Berkeley}, EECS, Berkeley, CA, United States, 2015.4 - 2017.5 \\
	      \begin{tabular}{ll}
		      Position: & Postdoctoral Researcher                                 \\
		      Project:  & Hierarchical decision-making and reinforcement learning \\
		      Adviser:  & Prof. Stuart Russell                                    \\
	      \end{tabular} \\
	\item \textbf{Carnegie Mellon University}, CSD, Pittsburgh, PA, United States, 2013.12 - 2015.3 \\
	      \begin{tabular}{ll}
		      Position: & Visiting Research Scholar                         \\
		      Project:  & Human-robot interaction and multi-object tracking \\
		      Adviser:  & Prof. Manuela Veloso and Prof. Reid Simmons       \\
	      \end{tabular} \\
	\item \textbf{University of Science and Technology of China}, CSD, Hefei, Anhui, China, 2009.9 - 2014.11 \\
	      \begin{tabular}{ll}
		      Position: & Research Assistant                              \\
		      Project:  & Hierarchical decision-making in RoboCup domains \\
		      Adviser:  & Prof. Xiaoping Chen                             \\
	      \end{tabular} \\
\end{itemize}

\vspace{10pt}
\section*{Education}
\begin{itemize}
	\item \textbf{University of Science and Technology of China}, Hefei, Anhui, China, 2009.9 - 2014.11 \\
	      Ph.D. in Computer Science, advised by Prof. Xiaoping Chen
	\item \textbf{University of Science and Technology of China}, Hefei, Anhui, China, 2005.9 - 2009.6 \\
	      B.E. in Computer Science
\end{itemize}

%\vspace{10pt}
%\section*{Research Interests}
%\begin{itemize}
%	\item Decision-theoretic Planning, Reinforcement Learning, Deep Learning, Computer Vision and Robotics
%\end{itemize}

\vspace{10pt}
\section*{Publications}
\nocite{*}
\bibliography{publications}
\bibliographystyle{plainyr}

\vspace{10pt}
\section*{Honors and Awards}
\begin{itemize}
	\item \textbf{World Champion} of Soccer Simulation 2D, RoboCup 2013, Eindhoven, The Netherlands, Jul 2013.
	\item \textbf{Champion} of Soccer Simulation 2D, RoboCup China Open 2012, Hefei, China, Dec 2012.
	\item \textbf{First Place} of Soccer Simulation 2D Free Challenge, RoboCup 2012, Mexico City, Mexico, Jun 2012.
	\item Second Place of Soccer Simulation 2D, RoboCup 2012, Mexico City, Mexico, Jun 2012.
	\item \textbf{Champion} of Soccer Simulation 2D, RoboCup China Open 2011, Lanzhou, China, Aug 2011.
	\item \textbf{World Champion} of Soccer Simulation 2D, RoboCup 2011, Istanbul, Turkey, Jul 2011.
	\item \textbf{Champion} of Soccer Simulation 2D, RoboCup China Open 2010, Ordos, China, Jul 2010.
	\item Second Place of Soccer Simulation 2D, RoboCup 2010, Singapore, Singapore, Jul 2010.
	\item \textbf{Champion} of Soccer Simulation 2D, RoboCup China Open 2009, Dalian, China, Nov 2009.
	\item \textbf{World Champion} of Soccer Simulation 2D, RoboCup 2009, Graz, Austria, Jun 2009.
	\item Second Place of Soccer Simulation 2D, RoboCup China Open 2008, Zhongshan, China, Dec 2008.
	\item Second Place of Soccer Simulation 2D, RoboCup 2008, Suzhou, China, Jul 2008.
	\item \textbf{Champion} of Soccer Simulation 2D, RoboCup China Open 2007, Jinan, China, Oct 2007.
\end{itemize}

\vspace{10pt}
\section*{Scholarships}
\begin{itemize}
	\item Early Researcher Support of ICAPS, 2014.
	\item Travel Award of NIPS Foundation, 2013.
	\item Glarun Scholarship of CETC-14, 2013.
	\item Scholarship of China Scholarship Council (CSC), 2013.
	\item Kwang-Hua Scholarship of USTC, 2012.
	\item Aegon-Industrial Responsibility Scholarship of USTC, 2012.
	\item Outstanding Student Scholarship of USTC, 2006, 2007, 2008.
	\item Outstanding Freshman Scholarship of USTC, 2005.
\end{itemize}

\vspace{10pt}
\section*{Professional Services}
\begin{itemize}
	\item \textbf{Reviewer}: AAMAS 2011-2013;2017, Agent CN 2012, AAAI 2012;2015, RoboCup 2012-2014, IAS 2013;2014, ACCV 2018, CVPR 2019, IEEE Intelligent Systems, Artificial Life and Robotics, Autonomous Robots
	\item \textbf{Programme Committee}: IJCAI 2015-2018, AAAI 2016-2019, RLDM 2017
	\item \textbf{Organizing Committee}: RoboCup 2012;2013, RoboCup China Open 2007-2012
	\item \textbf{Technical Committee}: RoboCup 2011, RoboCup China Open 2007-2012
\end{itemize}

\vspace{10pt}
\section*{Qualifications}
\begin{itemize}
	\item Strong research and engineering skills
	\item Rich \textbf{artificial intelligence}, \textbf{machine learning} and \textbf{robotics} experience
	\item Excellent interpersonal, communicating, writing, analytical and research skills
	\item Reliable, versatile, cooperative, good team member or independent worker
\end{itemize}

\vspace{10pt}
\section*{Technical Skills}
\begin{itemize}
	\item Proficiency in C/C++, Python, BASH and Java languages
	\item Rich Linux/UNIX, PyTorch, Tensorflow, Keras, OpenCV and ROS experience
	\item Expertise on planning, (deep) reinforcement learning and (deep) machine learning
\end{itemize}

\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
