\documentclass[fontsize=10pt]{tccv}
\usepackage[english]{babel}

\begin{document}

\part{Aijun Bai}

\section{Experience}

\begin{eventlist}

	\item{May 2017 | Present}
	      {Researcher, Microsoft Cloud \& AI}
	      {Cognition Intelligence}

	Developed reinforcement learning based pipeline optimization algorithms for computer vision tasks. Implemented in Python with PyTorch and applied on OCR and object detection pipelines with significant improvements. Publish in progress.

	\item{April 2015 | May 2017}
	      {Postdoctoral Researcher, UC Berkeley}
	      {Hierarchical Decision-Making}

	Developed Markovian state/action abstractions for MDPs via hierarchical MCTS.  Developed efficient concurrent hierarchical reinforcement learning algorithms. Implemented in C++ and achieved state-of-the-art results on RoboCup Keepaway task. Published 3 papers on \textbf{IJCAI} and \textbf{RoboCup Symposium}. Advised by Prof. Stuart Russell.

	\item{December 2013 | March 2015}
	      {Visiting Research Scholar, CMU}
	      {Human-Robot Interaction}

	Developed particle filtering over sets algorithm for multi-human tracking. Implemented in C++ with ROS and applied on CoBots -- mobile service robots of CMU. Published 2 papers on \textbf{AAAI Symposium} and \textbf{Fusion}. Advised by Prof. Manuela Veloso and Prof. Reid Simmons.

	\item{September 2009 | November 2014}
	      {Research Assistant, USTC}
	      {Hierarchical Online Planning}

	Developed hierarchical online planning algorithms for MDPs and POMDPs via MAX-Q decomposition. Implemented in C++ and applied on WrightEagle soccer simulation team in annual RoboCup competitions. Won 3 \textbf{World Champions} and 5 \textbf{National Champions}.  Published 6 papers on \textbf{NIPS}, \textbf{ICAPS}, \textbf{AAMAS}, \textbf{ACM Trans} and \textbf{RoboCup  Symposium}. Advised by Prof. Xiaoping Chen.

\end{eventlist}

\personal
{Redmond, WA 98052}
{+1 510 944 3906}
{aijun.bai@microsoft.com}

\section{Education}

\begin{yearlist}

	\item[Univ of Sci \& Tech of China]{2014}
        {Ph.D. in Computer Science}{}

	\item[Univ of Sci \& Tech of China]{2009}
        {B.E. in Computer Science}{}

\end{yearlist}

\section{Qualifications}

\begin{factlist}
	\item{$\bullet$}{Strong research and engineering skills}
	\item{$\bullet$}{ Rich \textbf{Artificial Intelligence}, \textbf{Machine Learning}, and \textbf{Robotics} experience}
	\item{$\bullet$}{Excellent interpersonal, communicating, writing and analytical skills}
	\item{$\bullet$}{Reliable, versatile, cooperative, good team member and independent worker}
\end{factlist}

\section{Technical skills}

\begin{factlist}
	\item{Coding}{C/C++, Python, BASH, Java}
	\item{Engineering}{Linux/UNIX, PyTorch, Tensorflow, Keras, ROS, OpenCV, NumPy}
	\item{Expertise}{Planning, (Deep) Reinforcement Learning, (Deep) Machine Learning, Computer Vision, Robotics}
\end{factlist}

\section{Links}

\begin{factlist}
	\item{Homepage}{\href{http://aijunbai.github.io/}{aijunbai.net}}
	\item{GitHub}{\href{https://github.com/aijunbai}{github.com/aijunbai}}
	\item{LinkedIn}{\href{https://www.linkedin.com/in/aijunbai}{linkedin.com/in/aijunbai}}
\end{factlist}

\end{document}
